Word learning at the semantics pragmatics interface

### 2020-04-08 paper/supplementary_material.Rmd
finish prediction section

We compared the models mentioned above in two ways. On the one hand, we used correlations between model predictions and the data. For this analysis, we binned the model predictions and the data by year and familiar object. Figure \@ref(fig:fig6) visualizes the correlation between model predictions and the data for all models. The results shows a very high correlation between the predictions of the *integration model* and the data in all age groups suggesting that the model accurately captures the variation in the data. The correlation increased from 2- to 3-year-olds but then again dropped for 4-year-olds. This is probably a consequence of the model making very extreme predictions for the oldest age group. Correlations for the *integration model* were also higher compared to the other models considered.

On the other hand, we compared models based on Bayes factors which were calculated from the marginal likelihoods of each model given the data. For this analysis, we treated age continuously. We first calculated the marginal log-likelihood for each model and then computed Bayes factors by subtracting the log-likelihoods for the models involved in the comparison and then exponentiating the result (see file `model_comparison.Rmd` in the associated online repository). Table \@ref(tab:table5) lists the Bayes factors for the different model comparisons. The results show that the *integration model*, by far, outperformed all the other models. When comparing the lesion models among each other, we see that models including the mutual exclusivity inference make better predictions compared to the *no mutual exclusivity model*.

Taken together, this analysis showed two things. First, the *integration model* makes accurate predictions about how mutual exclusivity and common ground inferences are integrated with one another. It does so based on knowing the strength and development of each inference alone. Second, models that omit one or more type of information (object specific word knowledge, speaker informativeness, common ground sensitivity) make much worse predictions. This exemplifies that children across the entire age range flexibly integrate all the available information. In the next section we ask whether there are other ways think about the process of information integration than the way formalized in the *integration model*.

>>>>

We compared the models mentioned above in two ways. On the one hand, we used correlations between model predictions and the data. For this analysis, we binned the model predictions and the data by age in years and familiar object. Figure \@ref(fig:fig6) visualizes the correlation between model predictions and the data for all models. The results shows a very high correlation between the predictions of the *integration model* and the data in all age groups suggesting that the model accurately captures the variation in the data. The correlation increased from 2- to 3-year-olds but then again dropped for 4-year-olds. The mis-match for the oldest age group is probably a consequence of the model making very extreme predictions for this group. [MH: Do we know why the model makes extreme predictions for the older age? Is it because they are at ceiling on the ME and/or common ground task, and our model posits no integration cost?] Correlations for the *integration model* were also higher compared to the other models considered.

We additionally compared models based on the marginal likelihood of the data under each model -- the likelihood of the data averaging over ("marginalizing over") the prior distribution on parameters; the pair-wise ratio of marginal likelihoods for two models is known as the Bayes Factor (see file `model_comparison.Rmd` in the associated online repository). Bayes Factors quantify the quality of predictions of a model, averaging over the possible values of the parameters of the models (weighted by their prior probability); by averaging over the prior distribution on parameters, Bayes Factor implicitly take into account model complexity because models with more parameters will tend to have a broader prior distribution over parameters, which in effect, can water down the possible better predictions that a model with more parameters can achieve (CITE: Lee & Wagenmakers 2014 Bayesian Cognitive Modeling). For this analysis, we treated age continuously. Table \@ref(tab:table5) lists the Bayes factors for the different model comparisons. The results show that the *integration model*, by far, outperformed all the other models. When comparing the lesion models among each other, we see that models including the mutual exclusivity inference make better predictions compared to the *no mutual exclusivity model*.

Taken together, these analyses showed two things. First, the *integration model* makes accurate predictions about how mutual exclusivity and common ground inferences are integrated. It does so based on knowing the strength and development of each inference alone, and incorporating them into a structured probabilistic model of pragmatic reasoning. Second, models that omit one or more types of information (object specific word knowledge, speaker informativeness, common ground sensitivity) make appreciably worse predictions. This result exemplifies that children across the entire age range flexibly integrate all the available information. In the next section we ask whether there are other ways think about the process of information integration than the way formalized in the *integration model*.
